Reliable Web Services Composition: A MDD Approach

### 2013-09-30 WESOA2013/source/paperSOAP_tosubmit.tex
inicial --martin

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
% 
% 1st. author
% \alignauthor
% Pl\'acido A. Souza Neto\\
% 	   \affaddr{Federal Institute of Rio Grande do Norte (IFRN)},\\
%        \affaddr{Federal University of Rio Grande do Norte (UFRN)}\\
%        \affaddr{Natal-RN, Brazil}\\
%        \email{placido.neto@ifrn.edu.br}
% \alignauthor Genoveva Vargar-Solar\\
%        \affaddr{French Council of Scientific Research}\\
%        \affaddr{LIG-LAFMIA }\\
%        \affaddr{Saint Martin d'H\`{e}res, France}\\
%        \email{Genoveva.Vargas-Solar@imag.fr}
% \alignauthor Valeria de Castro\\
%        \affaddr{Universidad Rey Juan Carlos}\\
%        \affaddr{M\'{o}stoles, Spain}\\ 
%        \email{Valeria.deCastro@urjc.es}
% \and
% \alignauthor Martin A. Musicante\\
%        \affaddr{Federal University of Rio Grande do Norte (UFRN)}\\
%        \affaddr{Natal-RN, Brazil}\\
%        \email{mam@dimap.ufrn.br}
% \alignauthor Jos\'e-Luis Zechinelli-Martini\\
%        \affaddr{Fundaci\'on Universidad de las Am\'ericas Puebla (UDLAP)}\\
%        \affaddr{San Andr\'es Cholula, M\'exico}\\
%        \email{joseluis.zechinelli@udlap.mx}
% \alignauthor Christine Collet\\
%        \affaddr{Grenoble Institute of Technology}\\
%        \affaddr{Saint Martin d'H\`{e}res, France}\\
%        \email{Christine.Collet@grenoble-inp.fr}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

@@

Service oriented development methodologies providing mod\-els, best practices,
and reference architectures to build services' based applications mainly address 
functional aspects \cite{1,2,decastro1,PapazoglouH06}.  Non-functional aspects
concerning services' and application's "semantics", often expressed as
requirements and constraints in general purpose methodologies, are not fully
considered or they are added once the application has been implemented in order 
to ensure some level of reliability (e.g., data privacy, exception handling,
atomicity, data persistence). This leads to services' based applications that
are partially specified and that are thereby partially compliant with
application requirements.

>>>>

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
% 
% 1st. author
% \alignauthor
% Pl\'acido A. Souza Neto\\
% 	   \affaddr{Federal Institute of Rio Grande do Norte (IFRN)},\\
%        \affaddr{Federal University of Rio Grande do Norte (UFRN)}\\
%        \affaddr{Natal-RN, Brazil}\\
%        \email{placido.neto@ifrn.edu.br}
% \alignauthor Genoveva Vargar-Solar\\
%        \affaddr{French Council of Scientific Research}\\
%        \affaddr{LIG-LAFMIA }\\
%        \affaddr{Saint Martin d'H\`{e}res, France}\\
%        \email{Genoveva.Vargas-Solar@imag.fr}
% \alignauthor Valeria de Castro\\
%        \affaddr{Universidad Rey Juan Carlos}\\
%        \affaddr{M\'{o}stoles, Spain}\\ 
%        \email{Valeria.deCastro@urjc.es}
% \and
% \alignauthor Martin A. Musicante\\
%        \affaddr{Federal University of Rio Grande do Norte (UFRN)}\\
%        \affaddr{Natal-RN, Brazil}\\
%        \email{mam@dimap.ufrn.br}
% \alignauthor Jos\'e-Luis Zechinelli-Martini\\
%        \affaddr{Fundaci\'on Universidad de las Am\'ericas Puebla (UDLAP)}\\
%        \affaddr{San Andr\'es Cholula, M\'exico}\\
%        \email{joseluis.zechinelli@udlap.mx}
% \alignauthor Christine Collet\\
%        \affaddr{Grenoble Institute of Technology}\\
%        \affaddr{Saint Martin d'H\`{e}res, France}\\
%        \email{Christine.Collet@grenoble-inp.fr}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

@@

Service oriented development methodologies providing mod\-els, best practices,
and reference architectures to build services' based applications mainly address 
functional aspects \cite{1,2,decastro1,PapazoglouH06,QueirozB12}. 
Non-functional aspects concerning services' and application's ``semantics'', often expressed as
requirements and constraints in general purpose methodologies, are not fully
considered or they are added once the application has been implemented in order 
to ensure some level of reliability (e.g., data privacy, exception handling,
atomicity, data persistence). This leads to services' based applications that
are partially specified and that are thereby partially compliant with
application requirements.
